\subsubsection{Questions for Understanding}
\begin{enumerate}
	\item If you add a file to an empty repository, is it tracked or
	   untracked?
	\item Can you add folders with the `git add` command?
	\item When running \verb`git status`, you can see that a file has been
			modified with changes to be committed, \emph{and} modified with
	   changes not staged for commit. What happened?
	\item When running \verb`git status -s`, what is the left column? The
	   right?
	\item What expression would you use to ignore all \verb`.pdf` files in a
	   repository in the \verb`.gitignore`?
	\item What's the difference between \verb`git diff` and \verb`git diff --cached`?
	\item If you use \verb`git commit` with no arguments, when does the
	   commit get created?
	\item If you modify a file or stage it, and then attempt to remove it
	   with \verb`git rm`,which flag must you add?
	\item To stop tracking a file but retain it in the working area, what
	   flag must you add to \verb`git rm`?
	\item Does git track whether files are renamed?
\end{enumerate}

\subsubsection{Exercises}
 Throughout the exercises, it is recommended that you routinely run
\verb`git status` in order to see how the repository views your changes.
Exercises should be done in order.
\begin{enumerate}
	\item Go to your recipes repository, which you made in the last chapter.
	   Create a file called \verb`README.txt`, and put a brief message in
	   it, perhaps, ``I like cookies." Stage, and then commit, the file.
	\item Create a file, \verb`cookies.txt`, and add some ingredients to it.
	   Stage the changes.
	   Then, go back to the file and add cooking instructions.
	   Commit your changes, stage the remaining ones, and then commit them.
	   This exercise is to reinforce the nature of the working and stagin
	   areas.
	\item Create a file, \verb`ignoreme.txt`, and set up the repository to
	   ignore it.
	   (Hint: you will need to commit changes to the \verb`.gitignore`).
	   Commit the changes to the \verb`.gitignore`.
	   Check the working area and \verb`git status` to verify that the file
	   is present, but ignored by the repository.
	\item Set up the repository to ignore all \verb`.pdf` and \verb`.docx`
	   files.
	\item Create a file, \verb`hello.txt`, with ``Hello, world!" in it,
	   and then commit it. Stop tracking it without deleting the file from
	   disk.
	   What does the status say after you do so?
	   After checking, unstage the change.
	\item Change \verb`hello.txt` to \verb`hello_world.txt` without using
	   \verb`git mv`.
	   Then, change it back using \verb`git mv`.
\end{enumerate}
