\subsubsection{Questions for Understanding}
\begin{enumerate}
	\item Why does rebasing appear to make the history cleaner?
	\item What will attract the scorn of friends and family?
	\item What are two cases in which rebasing is fine?
	\item Discuss the pros and cons of rebasing vs. merging.
\end{enumerate}

\subsubsection{Exercises}
Do exercises in order in the recipes repository.
\begin{enumerate}
	\item Clean rebase
	\begin{enumerate}
	   \item Make two branches, one called \verb`bread` and one called
	   \verb`sandwich`.
	   \item Create the \verb`sandwich` recipe while referencing the
	   incomplete \verb`bread`
		  recipe.
	   \item Switch to the \verb`bread` recipe and complete it.
	   \item Rebase \verb`bread` onto \verb`main` and merge it.
	   \item Rebase \verb`sandwich` onto \verb`main` and merge it.
	   \item View the history.
		  Note how it implies that \verb`bread` came first in history, even though
		  you actually made the sandwich recipes first.
	\end{enumerate}
	\item Scorn-inducing rebase
	\begin{enumerate}
	   \item Create a branch, \verb`broccoli`, with instructions on making broccoli.
		  Make sure the branch has several commits.
	   \item Push \verb`broccoli` to \verb`test` (as set up in the previous chapter).
	   \item Locally, rebase \verb`broccoli` onto \verb`main`.
	   \item Add an additional recipe on your \verb`broccoli` branch.
	   \item Attempt to push to the \verb`test` remote with your \verb`broccoli` branch.
	   \item Force-push the new \verb`broccoli` branch to the remote.
	   \item What would happen if somebody had already based new work after your
		  first push?
		  In this scenario, is it likely that something like that has happened?
		  What if the project was larger?
	\end{enumerate}
\end{enumerate}
