\subsection{About Version Control}
\begin{enumerate}
	\item What is the big weakness of Centralized Version Control?
	\item In distributed version control, why is there no longer one point
	    of failure?
\end{enumerate}

\subsection{A Short History of Git}
\begin{enumerate}
	\item Which community was motivated to create a new version control tool?
	\item When was Git created?
\end{enumerate}

\subsection{What is Git?}
\begin{enumerate}
	\item Does Git store snapshots or differences?
	\item Do you need to be online to use Git?
	\item What are the three states that files in a repository can reside
	    in?
\end{enumerate}

\subsection{The Command Line}

\begin{enumerate}
	\item Where is the only place you can run all Git commands?
\end{enumerate}


\subsection{Installing Git}

\begin{enumerate}
	\item What version of Git are you running?
\end{enumerate}

\subsection{First-Time Git Setup}

\begin{enumerate}
	\item What's the difference between \verb`--global` and \verb`--system` when running \verb`git config`?
	\item Why might you need to check your configuration settings?
	\item Set up your git config
	    \begin{enumerate}
		    \item Name
		    \item Email
	    \end{enumerate}
	\item Verify that your name is correctly configured with
	    `git config`
\end{enumerate}

\subsection{Getting Help}

\begin{enumerate}
	\item Use \verb`git help` to answer the following:
	    \begin{enumerate}
	    \item  Is \verb`git stash clean` a valid command?
	    \item  Is \verb`git stash drop` a valid command?
	    \item  What flags can be used to show the short version of \verb`git status`?
	    \end{enumerate}
\end{enumerate}
